A Switching Planner for Combined Task and Observation Planning

### 2010-11-29 code/subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/evaluation.tex
paper updates

\begin{figure}[h]
  \centering
  \input{figures/dora}
  \caption{A exploration domain with three rooms and 13 places. The
    robot is in in the centre of room A}
\label{fig:dora2}
\end{figure}
An instance of this domain is shown in figure \ref{fig:dora2}. Basic
types of element are {\tt rooms}, {\tt places} and {\tt
  objects}. Places are topological map nodes that occur in rooms.
Objects, including the robot, are always located at a place. The robot
can move around the rooms via connections between places given by the
{\tt connected} predicate. Each room has a, possibly unknown, {\em
  category} (e.g. kitchen, office, living room) and depending on this
category, objects are placed inside the rooms.

The robot can find out if an object is at a certain place by executing
the {\tt look-for-object} action. Moreover, the contents of a room
indicates its category, and certain objects are more likely to be
located in rooms of certain categories. For example, a box of
cornflakes is more likely to be located in the kitchen than the
office. The {\tt look-for-object} might result in a positive
perception if the object is there. An instantaneous positive detection
of the object is not proof positive that it is there. Also, some
objects are harder to detect than others. Also, Additionally, if the
robot is in the presence of a human, it can ask what type of room they
are currently in, however conducting a dialogue is more costly than
running a vision algorithm (cost of 8 vs costs of 3).

We perform experiments on tasks of several sizes. The robot's
objective is to find one or more objects and report back their
position to a person. In order to determine the impact of sensor
reliability in a comparison with the baseline, we also run tests on
identical problems but changed the sensor model for the target
objects: the probability for perceiving the object if it was there
went from 0.9 in the easiest case to 0.65 and 0.4 in the average and
hard cases respectively. In addition, we test how our system performs
in tasks requiring indirect sensing. Here, we gave the planner rewards
for visiting a certain type of room (e.g. kitchen or office). We did
not place any humans in those scenarios, so the only way of
determining the room category is by looking for objects typical for
that room type. As this indirect reasoning is a tasks that cannot be
performed by the continual planner alone, we did not run the baseline
system on those problems.

@@

Using a satisficing, optimistic serial planner in sequential sessions
makes optimising for the expected reward difficult. Only reasoning
about single traces, it is optimistic wrt the remaining costs to a
goal and pessimistic regarding the probability of reaching tat. By
setting the rewards to non-extremal values has little effect on that
system. Therefore, we do not consider expected utility in our
experiments. Instead, we report average costs of the plans and the
success rate (as a ratio between solved and solvable problems).

>>>>

% \begin{figure}[h]
%   \centering
%   \input{figures/dora}
%   \caption{A exploration domain with three rooms and 13 places. The
%     robot is in in the centre of room A}
% \label{fig:dora2}
% \end{figure}
% An instance of this domain is shown in figure \ref{fig:dora2}. 
Basic types of element are {\tt rooms}, {\tt places} and {\tt
  objects}. Places are topological map nodes that occur in rooms.
Objects, including the robot, are always located at a place. The robot
can move around the rooms via connections between places given by the
{\tt connected} predicate. Each room has a, possibly unknown, {\em
  category} (e.g. kitchen, office, living room) and depending on this
category, objects are placed inside the rooms.

The robot can look for an object at a place by executing a {\tt
  look-for-object} action. Moreover, the contents of a room indicate
its category, because certain objects are more likely to be located in
rooms of particular categories. For example, a box of cornflakes is
more likely to be located in the kitchen than the office. Executing
{\tt look-for-object} results in a noisy sensing outcome, sometimes
indicating a positive perception if the object is there. Here, some
objects are harder to detect than others. Lastly, if the robot is in
the presence of a human, it can ask what type of room it is currently
in, however conducting a dialogue is more costly than running a vision
algorithm (cost of 8 vs costs of 3).

%%  Therefore, an instantaneous positive detection of an object is
%% not proof positive of it being there.

We perform experiments on tasks of several sizes. The objective is to
find one or more objects and report their position to the user. In
order to determine the impact of the reliability of sensing in a
comparison with the baseline, we run tests on identical problems but
changed the sensor model for the target objects: the probability for
perceiving the object if it was there went from 0.9 in the easiest
case to 0.65 and 0.4 in the average and hard cases respectively. In
addition, we test how our system performs in tasks requiring indirect
sensing. Here, we gave the planner rewards for visiting a certain type
of room (e.g. kitchen or office). We did not place any humans in those
scenarios, so the only way of determining the room category is by
looking for objects typical for that room type. As this indirect
reasoning is a tasks that cannot be performed by the continual planner
alone, we did not run the baseline system on those problems.

@@

Using a satisficing, optimistic serial planner in sequential sessions
makes optimising for the expected reward difficult. Only reasoning
about single traces, it is optimistic wrt the remaining costs to a
goal and pessimistic regarding the probability of reaching it. By
setting the rewards to non-extremal values has little effect on that
system. Therefore, we do not consider expected utility in our
experiments. Instead, we report average costs of the plans and the
success rate (as a ratio between solved and solvable problems).

### 2010-11-29 code/subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/switching.tex
paper updates

We describe our approach that switches between sequential and
contingent sessions. As a continual planning approach, it proceeds by
interleaving planning and execution in a deterministic-action POMDP
described in DTPDDL. During a sequential session, planning is
performed by a ``classical'' system,\footnote{That is, a planner
designed to solve fully observable deterministic tasks.}  and
execution proceeds according to the {\em trace} computed by that
system. Taking the form of a classical plan, the trace specifies a
sequence of POMDP actions that achieve the agent's objectives in a
deterministic approximation, i.e., {\em determinisation}, of the
problem at hand. More precisely, the trace is an interleaved sequence
of POMDP actions and {\em assumptive} actions. The latter correspond
to assumptions the planner makes about the truth value of propositions
-- e.g. that a box of cornflakes is located in the kitchen at the
third plan step. These are called {\em applicability} assumptions if
the trace includes an action $\action$ that is not applicable with
probability $1$ at the belief-state
\bstate\ that the system is projected to be in when \action\ is
scheduled for execution, i.e., $\exists\state\in\states\;
\bstate(\state) > 0$ and $\poss(\action)\not\subseteq\state$. By
scheduling
\action,  the serial planner makes an assumption about the
observability of the precondition $\poss(\action)$.

@@

In a deterministic-action POMDP all the uncertainty in state and
action is expressed in the $(\pp{:init})$ DTPDDL declaration. Our
approach uses the structure of that, as it occurs in the problem
description, to define a set of state-assumptions available to
sequential planning.
%%
Writing \#\ if the value of a proposition is unspecified, for
$\pp{DORA}$ we have the following assumptions:

@@

In order to make assumptions available to the sequential planner, we
add one {\em assumptive} action $\assumptiveS{i}$ to the problem for
each element, $\prob_i (T_i)$, of each probabilistic term from
$(\pp{:init})$. The physics of these actions is as
follows. $\assumptiveS{i}$ can be executed if no $\assumptiveS{j}$,
$j \neq i$, has been executed from the same probabilistic term, and,
either $(\pp{probabilistic}~..\prob_i~(T_i)..)$ is in the root
conjunct, or it occurs in $T_k$ for some executed
$\assumptiveS{k}$. Also, a distinct assumption about a proposition
$\prop$ can only be made once, and must be sequenced before any POMDP
actions that have $\prop$ in their precondition or effect.
%%
In other words, an assumptive action
must be applied to make a truth assignment to \prop, and then that
truth assignment can be modified by the DTPDDL domain operators.
%%
%%
Executing $\assumptiveS{i}$ in $\state$ effects a transition to a
successor state $\state^{T_i}$ with probability $\prob_i$, and
$\state^\bot$ with probability $1 - \prob_i$. Here, $\state^{T_i}$ is
the union of $\state$ with atomic terms from $T_i$ and the proposition
denoting the undefined fact is deleted. For example, if the action
adds $(=(\pp{is-in}~\pp{box})~\pp{office})$, then it must delete
$(=(\pp{is-in}~\pp{box})~\#)$. State $\state^\bot$ is an added sink,
where $\forall\action$ $\reward(\state^\bot, \action) = 0$ and
$\transProb(\state^\bot, \action, \state^\bot) = 1$.
%%
Lastly, we have that if $\action$ has a precondition that is not true
with probability $\theta$, a given threshold, in the underlying belief
$\bstate$, then immediately before it is executed blindly, the system
switches to a contingent session, discussed in the following section.

@@

\[
\reward(\state, \assumptiveDT{i}) = \bigg\{ \begin{array}{ll}
\$(T_i) & \pp{if}~\;\;T_i \not\subseteq \state \\
-\$(T_i) & \pp{otherwise} \\
\end{array}
\]

\noindent where $\$(T_i)$ is a positive numeric quantity which
captures the reward the agent receives for correctly rejecting a
false assumption. The added dual actions are propositionally trivial
-- i.e., $\forall\state\in\states$ $\poss(\assumptiveDT{i})
\subseteq \state$ and $\assumptiveDT{i}(\state) \equiv \state$.  
%%
In order to reduce the number of possible rejections we omit
assumptions that are not {\em active} with respect to the action,
\switchAction, whose scheduled execution switched the system into
the contingent session. An assumption $\assumptiveS{i}$ is active if
\switchAction\ is not applicable in the sequential model unless
$\assumptiveS{i}$ is scheduled in the trace prefix
to \switchAction. For example, if $\pp{DORA}$'s trace is:

@@

\[
\reward(\state, \actions.\poss(\switchAction)) = \bigg\{ \begin{array}{ll}
\$(\poss(\switchAction)) & \pp{if}~\;\; \poss(\switchAction) \subseteq \state \\
-\$(\poss(\switchAction)) & \pp{otherwise} \\
\end{array}
\]

For the purposes of successive switching, execution of either a dual
action of the form $\assumptiveDT{i}$, or the
$\actions.\poss(\switchAction)$, returns control to a sequential
session. If a dual is executed, then the sequential planner must
replan with $\bstate_0$ equal to the underlying
belief-state. Otherwise, if $\actions.\poss(\switchAction)$ is
executed, then the current sequential plan is executed until further
sensing is scheduled, or to completion. Lastly, we note that in our
project the rewards, i.e., function $\$:2^\propositions\to\Re$, for
the POMDP posed to the contingent session are sourced from a
motivational component of our robotic architecture. We make no
assumptions here about how they are derived.

The starting belief-state for the abstract process is given in terms
of a {\em relaxed} $(\pp{:init})$ declaration.  We first construct a
tree which only includes terms from the {\em relaxed} visitation
characterised by the active {\em assumptive} actions in the current
sequential plan. Taking our example trace from earlier, we have a {\em
relaxed} declaration:

\small
\begin{tabtt}
(\=:init (= (is-in DORA) kitchen) \+ \\
       (probabilistic \=.8 (= (is-in box) office)  \\
		      \>.2 (= (is-in box) kitchen))) \\
\end{tabtt}
\normalsize

\noindent and therefore, the belief-state $\bstate_0$ is:

\small
\begin{tabular}{cccc}
\hline
Probability & (is-in DORA)  & (is-in box)  & (is-in cup) \\
\hline
.8 & kitchen & office & \# \\
.2 & kitchen & kitchen & \# \\
\hline
\end{tabular}
\normalsize

\noindent At this point, the session would proceed in an
abstraction of the environment that does not contain a
$\pp{cup}$. With regards to abstraction, the contingent and serial
sessions apply the same applicability conditions ---i.e., that each
effect and condition $\prop$ is specified, $\prop\in\state$--- to
actions from the DTPDDL problem description.

In a second step, we iteratively refine the relaxed declaration by
adding terms from the original statement of $(\pp{:init})$ while the
number of abstract states that occur with non-zero probability
according to that refined declaration remains of a practicable
size. In detail, for each excluded atomic term, we compute the {\em
entropy} of the active assumptions, {\em conditional} on the
corresponding proposition. Loosely speaking, the {\em conditional
entropy} measure is higher the more uncertain those assumptions are
given truth assignment to the proposition. Propositions that in the
first place were excluded are iteratively added to the problem posed
to the conditional session in increasing order according to that
measure.

@@

>>>>

We describe our approach that switches between sequential and
contingent sessions. As a continual planning approach, it proceeds by
interleaving planning and execution in a deterministic-action POMDP
described in DTPDDL. During a sequential session, planning is
performed by a ``classical'' system,\footnote{That is, a planner
designed to solve fully observable deterministic tasks.}  and
execution proceeds according to the {\em trace} computed by that
system. Taking the form of a classical plan, the trace specifies a
sequence of POMDP actions that achieve the agent's objectives in a
deterministic approximation, i.e., {\em determinisation}, of the
problem at hand. More precisely, the trace is an interleaved sequence
of POMDP actions and {\em assumptive} actions. The latter correspond
to assumptions the planner makes about the truth value of propositions
-- e.g. that a box of cornflakes is located in the kitchen at the
third plan step. They are called {\em applicability} assumptions if
the trace includes an action $\action$ that is not applicable with
probability $1$ at the belief-state
\bstate\ that the system is projected to be in when \action\ is
scheduled for execution, i.e., $\exists\state\in\states\;
\bstate(\state) > 0$ and $\poss(\action)\not\subseteq\state$. By
scheduling
\action,  the serial planner makes an assumption about the
observability of the precondition $\poss(\action)$.

@@

In a deterministic-action POMDP all the uncertainty in state and
action is expressed in the $(\pp{:init})$ declaration. Our approach
uses the structure of that, as it occurs in the problem description,
to define a set of state-assumptions available to sequential planning.
%%
Writing \#\ if the value of a proposition is unspecified, for
$\pp{DORA}$ we have the following assumptions:

@@

In order to make assumptions available to the sequential planner, we
add one {\em assumptive} action $\assumptiveS{i}$ to the problem for
each element, $\prob_i (T_i)$, of each probabilistic term from
$(\pp{:init})$. The physics of these actions is as
follows. $\assumptiveS{i}$ can be executed if no $\assumptiveS{j}$,
$j \neq i$, has been executed from the same probabilistic term, and,
either $(\pp{probabilistic}~..\prob_i~(T_i)..)$ is in the root
conjunct, or it occurs in $T_k$ for some executed
$\assumptiveS{k}$. Also, an assumption about a proposition
$\prop$ can only be made once, and must be sequenced before any POMDP
actions that have $\prop$ in their precondition or effect.
%%
In other words, an assumptive action
must be applied to make a truth assignment to \prop, and then that
truth assignment can be modified by the DTPDDL domain operators.
%%
%%
Executing $\assumptiveS{i}$ in $\state$ effects a transition to a
successor state $\state^{T_i}$ with probability $\prob_i$, and
$\state^\bot$ with probability $1 - \prob_i$. Here, $\state^{T_i}$ is
the union of $\state$ with atomic terms from $T_i$ with the
proposition denoting the undefined fact is deleted. For example, if
the action adds $(=(\pp{is-in}~\pp{box})~\pp{office})$, then it must
delete $(=(\pp{is-in}~\pp{box})~\#)$. State $\state^\bot$ is an added
sink, where $\forall\action$ $\reward(\state^\bot, \action) = 0$ and
$\transProb(\state^\bot, \action, \state^\bot) = 1$.
%%
Lastly, we have that if $\action$ has a precondition that is not true
with probability $\theta$, a given threshold, in the underlying belief
$\bstate$, then immediately before it is executed blindly the system
switches to a contingent session (described below).

@@

\[
\reward(\state, \assumptiveDT{i}) = \bigg\{ \begin{array}{ll}
\$(T_i) & \pp{if}~\;\;T_i \not\subseteq \state \\
\hat\$(T_i) & \pp{otherwise} \\
\end{array}
\]

\noindent where $\$(T_i)$ (resp. $\hat\$(T_i)$) is a positive
(negative) numeric quantity which captures the utility the agent
receives for correctly (incorrectly) rejecting a false assumption. The
added dual actions are propositionally trivial -- i.e.,
$\forall\state\in\states$ $\poss(\assumptiveDT{i})
\subseteq \state$ and $\assumptiveDT{i}(\state) \equiv \state$.  
%%
In order to reduce the number of possible rejections we omit
assumptions that are not {\em active} with respect to the action,
\switchAction, whose scheduled execution switched the system into
the contingent session. An assumption $\assumptiveS{i}$ is active if
\switchAction\ is not applicable in the sequential model unless
$\assumptiveS{i}$ is scheduled in the trace prefix
to \switchAction. For example, if $\pp{DORA}$'s trace is:

@@

\[
\reward(\state, \actions.\poss(\switchAction)) = \bigg\{ \begin{array}{ll}
\$(\poss(\switchAction)) & \pp{if}~\;\; \poss(\switchAction) \subseteq \state \\
\hat\$(\poss(\switchAction)) & \pp{otherwise} \\
\end{array}
\]

For the purposes of successive switching, execution of either a dual
action of the form $\assumptiveDT{i}$, or the
$\actions.\poss(\switchAction)$, returns control to a sequential
session. If a dual is executed, then the sequential planner must
replan with $\bstate_0$ equal to the underlying
belief-state. Otherwise, if $\actions.\poss(\switchAction)$ is
executed, then the current sequential plan is executed until further
sensing is scheduled, or to completion. Lastly, we note that in our
project the rewards, i.e., functions
$\$,\hat\$:2^\propositions\to\Re$, for the POMDP posed to the
contingent session are sourced from a motivational component of our
robotic architecture. For this paper, we set $\$(x)$ to be a positive
constant, and have $\hat\$(x)= - \$(x)(1 - p) / p$ where $p$ is the
probability that $x$ is true.

%%  We make no assumptions here about how they are
%% derived.

The starting belief-state for the abstract process is given in terms
of a {\em relaxed} $(\pp{:init})$ declaration. We first construct a
tree which only includes terms from the {\em relaxed} visitation
characterised by the active {\em assumptive} actions in the current
sequential plan. Figure \ref{fig:abstraction} shows the belief state
of a more detailed version of our previous example. The diamonds
represent probabilistic terms of the state description while circles
represent conjunctive or atomic terms.

\begin{figure}[h!]
  \centering
  \tikzstyle{tree} = [sibling distance=4mm]
  \tikzstyle{toplevel} = [grow'=right, sibling distance=18mm]
  \tikzstyle{seclevel} = [sibling distance=8mm]
  \tikzstyle{pnode} = [diamond, draw=black, minimum size=2mm]
  \tikzstyle{cnode} = [circle, draw=black, minimum size=2.5mm]
  \tikzstyle{assumption} = [solid, thick, draw=black]
  \tikzstyle{selected} = [solid, draw=black]
  \tikzstyle{unused} = [densely dashed, draw=black!40]
  \subfloat[The initial belief state with the assumptions made by the continual
    planner.]{
      \label{fig:abstraction-a}
      \begin{tikzpicture}[
    level 3/.style={tree}]
    \node[pnode, assumption] (cat) at (1,1) {} [toplevel]
      child[seclevel] {node[cnode, assumption] (office) {}
        child {node [pnode, assumption] (box) {}
          child {node [cnode] (boxp1) {}}
          child {node [cnode, assumption] (boxp2) {}}
        }
        child {node [pnode] (cup) {} 
          child {node [cnode] (cupp1) {}}
          child {node [cnode] (cupp2) {}}
        }
      }
      child {node[cnode] (kitchen) {}
        child {node [pnode] (box2) {} 
          child {node [cnode] (box2p1) {}}
          child {node [cnode] (box2p2) {}}
        }
      };
   \tiny
   \draw[assumption] (cat) -- (office) -- (box) -- (boxp2);
   \node[above=0 of cat] {$\pp{(category room1)}$};
   \node[below=0 of kitchen] {$\pp{kitchen}$};
   \node[below=0 of office] {$\pp{office}$};
   \node[below=0 of box] {$\pp{(is-in box)}$};
   \node[below=0 of box2] {$\pp{(is-in box)}$};
   \node[below=0 of cup] {$\pp{(is-in cup)}$};
   \node[right=0 of boxp1] {$\pp{place1}$};
   \node[right=0 of boxp2] {$\pp{place2}$};
   \node[right=0 of box2p1] {$\pp{place1}$};
   \node[right=0 of box2p2] {$\pp{place2}$};
   \node[right=0 of cupp1] {$\pp{place1}$};
   \node[right=0 of cupp2] {$\pp{place2}$};
    % \node[node] (kitchen) right of (cat) {};
  \end{tikzpicture}}
\qquad
  \subfloat[Remove facts that are not part of an assumption.]{
    \label{fig:abstraction-b}
    \begin{tikzpicture}[
    level 3/.style={tree}]
    \node[pnode, assumption] (cat) at (1,1) {} [toplevel, unused]
      child[seclevel] {node[cnode, assumption] (office) {}
        child {node [pnode, assumption] (box) {}
          child {node [cnode, unused] (boxp1) {}}
          child {node [cnode, assumption] (boxp2) {}}
        }
        child {node [pnode, unused] (cup) {} 
          child {node [cnode, unused] (cupp1) {}}
          child {node [cnode, unused] (cupp2) {}}
        }
      }
      child {node[cnode, selected] (kitchen) {}
        child {node [pnode, selected] (box2) {} 
          child {node [cnode, unused] (box2p1) {}}
          child {node [cnode, selected] (box2p2) {}}
        }
      };
   \draw[assumption] (cat) -- (office) -- (box) -- (boxp2);
   \draw[selected] (cat) -- (kitchen) -- (box2) -- (box2p2);
   \tiny
   \node[above=0 of cat] {$\pp{(category room1)}$};
   \node[below=0 of office] {$\pp{office}$};
   \node[below=0 of box] {$\pp{(is-in box)}$};
   \node[below=0 of box2] {$\pp{(is-in box)}$};
   \node[right=0 of boxp2] {$\pp{place2}$};
   \node[right=0 of box2p2] {$\pp{place2}$};
    % \node[node] (kitchen) right of (cat) {};
  \end{tikzpicture}}
\qquad
  \subfloat[Re-add relevant facts until the belief space limit is reached.]{
    \label{fig:abstraction-c}
    \begin{tikzpicture}[
    level 3/.style={tree}]
    \node[pnode, assumption] (cat) at (1,1) {} [toplevel, unused]
      child[seclevel] {node[cnode, assumption] (office) {}
        child {node [pnode, assumption] (box) {}
          child {node [cnode, selected] (boxp1) {}}
          child {node [cnode, assumption] (boxp2) {}}
        }
        child {node [pnode, unused] (cup) {} 
          child {node [cnode, unused] (cupp1) {}}
          child {node [cnode, unused] (cupp2) {}}
        }
      }
      child {node[cnode, selected] (kitchen) {}
        child {node [pnode, selected] (box2) {} 
          child {node [cnode, selected] (box2p1) {}}
          child {node [cnode, selected] (box2p2) {}}
        }
      };
   \draw[assumption] (cat) -- (office) -- (box) -- (boxp2);
   \draw[selected] (box) -- (boxp1);
   \draw[selected] (cat) -- (kitchen) -- (box2) -- (box2p2);
   \draw[selected] (box2) -- (box2p1);
   \tiny
   \node[above=0 of cat] {$\pp{(category room1)}$};
   \node[below=0 of office] {$\pp{office}$};
   \node[below=0 of box] {$\pp{(is-in box)}$};
   \node[below=0 of box2] {$\pp{(is-in box)}$};
   \node[right=0 of boxp1] {$\pp{place1}$};
   \node[right=0 of boxp2] {$\pp{place2}$};
   \node[right=0 of box2p1] {$\pp{place1}$};
   \node[right=0 of box2p2] {$\pp{place2}$};
    % \node[node] (kitchen) right of (cat) {};
  \end{tikzpicture}}

  \caption{Generating the abstract belief space.}
\label{fig:abstraction}
\end{figure}

% \small
% \begin{tabtt}
% (\=:init (= (is-in DORA) kitchen) \+ \\
%        (probabilistic \=.8 (= (is-in box) office)  \\
% 		      \>.2 (= (is-in box) kitchen))) \\
% \end{tabtt}
% \normalsize

% \noindent and therefore, the belief-state $\bstate_0$ is:

% \small
% \begin{tabular}{cccc}
% \hline
% Probability & (is-in DORA)  & (is-in box)  & (is-in cup) \\
% \hline
% .8 & kitchen & office & \# \\
% .2 & kitchen & kitchen & \# \\
% \hline
% \end{tabular}
% \normalsize

 % With
% regards to abstraction, the contingent and serial sessions apply the
% same applicability conditions ---i.e., that each effect and condition
% $\prop$ is specified, $\prop\in\state$--- to actions from the DTPDDL
% problem description.

In the first step, we remove all facts that are not part of an
assumption (Fig. \ref{fig:abstraction-b}). At this point, the session
would proceed in an abstraction of the environment where that does not
contain $\pp{place2}$, the $\pp{cup}$ or a $\pp{kitchen}$.

In a second step, we iteratively refine the relaxed declaration by
adding terms from the original statement of $(\pp{:init})$ while the
number of abstract states in $\bstate_0$ that occur with non-zero probability
according to that refined declaration remains of a practicable
size. In detail, for each excluded atomic term, we compute the {\em
  entropy} of the active assumptions, {\em conditional} on the
corresponding proposition.  Loosely speaking, the lower the {\em
  conditional entropy} of an atom is, the more information about the
assumptions can the contingent planner expect to derive from it. Thus,
propositions that in the first place were excluded are iteratively
added to the problem posed to the conditional session in increasing
order according to that measure (Fig. \ref{fig:abstraction-c}).

@@

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "moritz_2011"
%%% End:
